\documentclass[a4paper]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\usepackage{xeCJK}
\usepackage[scale=0.9]{geometry}
\geometry{a4paper,top=2cm,bottom=1cm}
\name{Dong}{Chenyang}
\phone[mobile]{188~1159~9628}
\email{dongcy2018@econ.pku.edu.cn}

\begin{document}
\small{
    \maketitle
}
\section{Education}
\subsection{Peking University}
\cventry{2022 -- 2024}{Risk Management and Insurance}{School of Economics}{Master's}{}{
    \cvitem{GPA}{GPA 3.7/4, Top 20\%}
    \cvitem{Honors}{Peking University Third-Class Scholarship, Outstanding Student Award}
}
\subsection{Peking University}
\cventry{2018 -- 2022}{Risk Management and Insurance}{School of Economics}{Bachelor's}{}{
    \cvitem{GPA}{GPA 3.73/4, Top 20\%, Admitted to graduate school without entrance exam}
}
\section{Internship Experience}
\subsection{Guangfa Fund}
\cventry{2023/7 -- 2023/8}{Research and Development Department}{Industry Research}{}{}{
    \begin{itemize}
        \item \textbf{Elastic N.V.}: AI applications will drive Elastic's turnaround, expecting FY24 to miss consensus while FY25 beats, recommend holding
              \begin{itemize}
                  \item \textbf{Vector Database: Potential Leader in a Strong Industry}. Aligned with AI applications, TAM $6.4$ billion. Expected to gain 10\%-15\% market share due to stability and service capabilities.
                  \item \textbf{Observability: Survivor in a Weak Industry}. Pressured by slowing cloud spending, but unlikely to decline due to open source positioning and AI catalyst.
                  \item \textbf{Potential Catalysts}: Serverless will drive open-source user conversion; AI Assistant and OTel standards will address analysis shortcomings, gaining market share through open source and low prices.
              \end{itemize}
    \end{itemize}
}
\subsection{Zhongou Fund}
\cventry{2023/5 -- 2023/6}{Research Department}{Industry Research}{}{}{
    \begin{itemize}
        \item \textbf{Sangfor Tech}: Competition in the network security industry has shifted from product strength to channel capabilities, strategic control of channels intensifies, and the competitive environment improves marginally, recommending holding
              \begin{itemize}
                  \item \textbf{Short-term Fundamental Recovery with High Certainty}: Marginal improvement in the competitive environment, and the company's aggressive genes determine its ability to solve problems by increasing control over channels.
                  \item \textbf{Medium to Long Term, Security SaaS is Expected to Reshape Valuation}: Sangfor Tech has customer access advantages, and the current core contradiction lies in penetrating the core customer group.
              \end{itemize}
    \end{itemize}
}
\subsection{Guangfa Fund}
\cventry{2023/1 -- 2023/4}{Research and Development Department}{Industry Research}{}{}{
    \begin{itemize}
        \item \textbf{AI Special Report Series}: The most crucial aspects of large models are data and computing power, followed by talent, engineering capabilities, and models. The AI Governance and Compliance era arrived before ChatGPT.
              \begin{itemize}
                  \item \textbf{Model Layer}: ChatGPT represents the commercialization of large models rather than a singularity moment for AI models. Google's technology remains leading, with insufficient time for data and fine-tuning.
                  \item \textbf{Hardware Layer}: Nvidia has built a moat in the GPGPU field through optimized software-hardware integration, ten years of investment in the ecosystem, and full-process development coverage.
                  \item \textbf{Software Layer}: Calling APIs and prompt engineering are challenging to become competitive advantages; AI frameworks are gradually unifying, and AI development tools are entering a golden age.
              \end{itemize}
        \item \textbf{TEAM: From Agile Development, DevOps to MLOps}: Despite the impact of macroeconomic demand weakness, the company's fundamentals remain solid, and the conversion of free users is sustainable.
              \begin{itemize}
                  \item \textbf{Different Viewpoints from the Market}: The conversion flywheel is affected by macroeconomic and tech company layoffs, project management is a must in software development, and paid users will continue to grow sustainably.
                  \item \textbf{Competitive Advantages}: Jira's high integration becomes the core of the DevOps workflow, data accumulation improves user stickiness, and the conversion flywheel significantly reduces marketing expenses.
                  \item \textbf{Future Growth}: MLOps manages the ML application lifecycle, essentially based on DevOps, and may become a new growth curve for the company in the AI era.
              \end{itemize}
        \item Other research work: Heavy Truck Industry (PCAR); SaaS Industry (BILL, CFLT, FROG, PD, AI, WIX, GDDY, etc.)
    \end{itemize}
}

\subsection{CICC}
\cventry{2022/7 -- 2022/11}{Internet Group}{Industry Research}{}{}{
    \begin{itemize}
        \item \textbf{Tencent Holdings: An Observational Framework}: Tencent is expected to move towards a paradigm of slow revenue growth, fast profit growth, and even faster EPS growth, resembling a value stock.
        \item \textbf{Web3.0 Community Foundation, Ethereum Upgrade Imminent}: Public chains take on the role of basic infrastructure, and it is expected to form a situation where one (Ethereum) dominates and many (other public chains) are strong.
        \item Other research work: Tencent Holdings 3Q22 Performance Review; CICC Overseas Outlook: BeReal\&Gas; Online Content Platforms Review - 2Q22, etc.
    \end{itemize}
}
\section{Extracurricular Activities and Skills}
\cvitem{2021 Risk and Insurance Management Society (RIMS) Annual Summit Case Competition}{\small Made it to the global top eight as the only team from a non-U.S. institution}
\cvitem{"One Table" Volunteer Teaching Program}{\small During the early stages of the 2020 pandemic, served as one of the first volunteer teachers, tutoring the children of medical staff in Wuhan online}
\cvitem{Huaiyuan Project Summer Practice}{\small Went to a primary school in Muer Township, Gansu Province for two months of teaching and investigation}
\cvitem{Skills}{\small Python, Wind, Office, C/C++, R, SQL, Solidity, JavaScript, Bloomberg, Tableau, etc.}
\end{document}

